Risk Perceptions for Wearable Devices

### 2015-03-06 tex-inputs/results-recipient.tex

\subsubsection{Data Recipient}
There was a statistically significant difference in VUR for an application's servers comparatively to human data recipients. 42\% of participants stated that they would be ``very upset'' if their data was shared with only the app's servers, whereas the VURs for friends (70\%), work contacts (75\%), and the public (72\%) were much higher (Table \ref{recipient-vur}). A chi-square test indicated that these differences were statistically significant (Table \ref{recipient-chi}). However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).

>>>>

\subsubsection{Data Recipient}
There was a statistically significant difference in VUR for data sent to an application's servers compared to data sent to human recipients. On average, 42\% of participants stated that they would be ``very upset'' if their data was shared with only an application's servers, whereas the VURs for friends (70\%), work contacts (75\%), and the public (72\%) were much higher (Table \ref{recipient-vur}). A chi-square test indicated that these differences were statistically significant (Table \ref{recipient-chi}). However, these effect sizes were small: the largest effect was between work contacts and an app's server ($\phi=0.11$); while the VUR for sharing with work contacts was significantly higher than sharing with friends, the effect size was negligible ($\phi=0.004$).
